Numerical modelling of the Cordilleran ice sheet

### 2014-07-18 kappa.tex
Implement comments from Arjen.

\begin{description}
  \item[\CCLI] \bibentry{Seguinot.etal.2014}.
  \item[\PSDV] \bibentry{Seguinot.2013}.
  \item[\PSDP] \bibentry{Seguinot.Rogozhina.2014}.
  \item[\CCYC] \bibentry{Seguinot.etal.manuscript}.\renote{
    Arjen, you had several comments regarding the style of references
    throughout the kappa (name formatting, italic text). I am using the
    Copernicus style here, but is there another recommendation to follow?
    Maybe Peter knows?}
\end{description}

@@

\footnotesize{\begin{enumerate}
  \item[I] A.~P.~Stroeven initiated the Cordilleran ice sheet modelling
project; I set-up the ice sheet model (PISM) and supercomputing workflow, ran
simulations and wrote the first draft; C.~Khroulev implemented necessary code
changes in the model; I.~Rogozhina contributed to experiment design; A.~P.~Stroeven
helped with interpretation of the results; and Q.~Zhang prepared some of the
forcing data. All co-authors contributed to improve the text.
  \item[II] I analysed the weather data, wrote the positive degree day model
(PyPDD), ran computations and wrote the manuscript. A.~P.~Stroeven contributed
with editorial comments at the pre-submission stage and I.~Rogozhina helped to
assess the reviews.
  \item[III] I.~Rogozhina provided the original idea; I analysed the weather
data and developed a new parameterization of daily temperature standard
deviation. I.~Rogozhina and I wrote the manuscript. A.~P.~Stroeven contributed
with editorial comments at the pre-submission stage.
  \item[IV] I integrated the new parameterization of standard deviation into
PISM, ran the simulations and wrote the first draft; I.~Rogozhina guided
experiment design; A.~P.~Stroeven, M.~Margold and J.~Kleman took part in the
interpretation and comparison of model results against geological evidence. All
co-authors contributed to improve the text.
\end{enumerate}}

@@

Next to the atmospheric forcing, another critical source of uncertainty in
palaeo-ice sheet modelling is the choice of parameters used by the surface mass
balance model \citep[e.g.,][]{Hebeler.etal.2008}. In our case, these parameters
are the degree-day factors for snow, $F_s$, and ice, $F_i$
(\cref{fig:model-pdd,tab:surfaceparams}), and the standard deviation of
near-surface air temperature,$\sPDD$
(\cref{eqn:calovgreve,tab:surfaceparams}). Although the first two can only be
deduced from surface mass-balance measurements on present-day glaciers
\citep[e.g.,][]{Shea.etal.2009} and assumptions that these values are also
valid for palaeo-simulations, $\sPDD$ can be estimated from temperature time
series \citep[e.g.,][]{Fausto.etal.2011}.

@@

\noindent\textbf{\CCYC} --- \bibentry{Seguinot.etal.manuscript}.
\bigskip

>>>>

\begin{description}
  \item[\CCLI] \bibentry{Seguinot.etal.2014}
  \item[\PSDV] \bibentry{Seguinot.2013}
  \item[\PSDP] \bibentry{Seguinot.Rogozhina.2014}
  \item[\CCYC] \bibentry{Seguinot.etal.inpreparation}
\end{description}

@@

\small{\begin{enumerate}
  \item[I] I set-up the ice sheet model and supercomputing workflow, ran the
simulations and wrote the manuscript; C.~Khroulev implemented necessary code
changes in PISM; I.~Rogozhina guided experiment design; A.~P.~Stroeven
initiated the Cordilleran ice sheet modelling project; and Q.~Zhang prepared
some of the forcing data. All co-authors contributed to improve the text.
  \item[II] I analysed the weather data, wrote the positive degree day model,
ran computations and wrote the manuscript. I.~Rogozhina helped to assess the
reviews.
  \item[III] I.~Rogozhina provided the original idea; I analysed the weather
data; and we wrote the manuscript together.
  \item[IV] I implemented necessary code changes in PISM, ran the simulations
and wrote the manuscript; I.~Rogozhina guided experiment design; M.~Margold,
J.~Kleman and A.~P.~Stroeven took part in the interpretation. All authors
contributed to improve the text.
\end{enumerate}}

@@

Next to the atmospheric forcing, another critical source of uncertainty in
palaeo-ice sheet modelling is the choice of parameters used by the surface mass
balance model \citep[e.g.,][]{Hebeler.etal.2008}. In our case, these parameters
are the degree-day factors for snow, $F_s$, and ice, $F_i$
(\cref{fig:model-pdd, tab:surfaceparams}), and the standard deviation of
near-surface air temperature, $\sPDD$ (\cref{eq:calovgreve,
tab:surfaceparams}). Although the first two can only be deduced from surface
mass-balance measurements on present-day glaciers
\citep[e.g.,][]{Shea.etal.2009} and assumptions that these values are also
valid for palaeo-simulations, $\sPDD$ can be estimated from temperature time
series \citep[e.g.,][]{Fausto.etal.2011}.

@@

\noindent\textbf{\CCYC} --- \bibentry{Seguinot.etal.inpreparation}.
\bigskip
